\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-11-22 jss/article.tex
just process.png to go!

\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
A hyper-prior distribution is a distribution assigned to the second-level parameters. With the goal of objectivity in mind our choice for hyper-priors assumes the following non-informative distributions:
\begin{equation}
\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
\end{equation}

@@

The Poisson model can have such posterior propriety if there are two groups whose observed values exceed 0 and the second-level mean ($\lambda_0$) is known. If $\lambda_0$ is unknown, the posterior distribution for the Poisson model is improper and this model should not be used. In the case where the Poisson model is as an approximation to the Binomial and the exposures, $n_j$, are known then the Binomial model should be used as an alternative to the Poisson. The efficiency of these priors is explored in the examples in section 5.

>>>>

\subsection[Hyper-prior Distribution]{Hyper-prior Distribution}
A hyper-prior distribution is a distribution assigned to the second-level parameters. With the goal of objectivity in mind our choice for hyper-priors assumes the following non-informative distributions:
\begin{equation}
  \label{eq:hyper}
\beta \sim \textrm{Uniform on}~ \mathbf{R}^{m}~~\textrm{and}~~A \sim \textrm{Uniform}(0, \infty) ~~(\textrm{or} ~\frac{1}{r}\sim \textrm{Uniform}(0, \infty)),
\end{equation}

@@

The Poisson model with hyper-prior in (\ref{eq:hyper}) provides posterior propriety if there are two groups whose observed values exceed 0 and the second-level mean ($\lambda_0$) is known ($m=0$). However, if $\lambda_0$ is unknown $(m \geq 1)$ the posterior distribution for the Poisson model is improper with hyper-prior in (\ref{eq:hyper}) and this model should not be used. In cases where the Poisson model is used because it is an approximation to the Binomial, then we recommend staying with the Binomial model with the same hyper-prior distribution. The efficiency of these priors is explored in the examples in section 5.
